Sparse spectral and $p$-finite element methods on disk-slices and trapeziums I: zero boundary conditions

### 2019-04-03 papers/halfdisk/halfdisk.tex
Edits to trapezium section

We can further extend this work to trapezium shaped domains. Note that for any trapezium there exists an affine map to the canonical trapezium domain that we consider here, given by
\begin{align}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align}
with 
\begin{align}
\begin{cases}
(\alpha, \beta) &:= (0,1) \\
(\gamma, \delta) &:= (0,1) \\
\rho(x) &:= 1-\half x \\
w^{(a,b,c)}_H(x) &:= (x - \alpha)^{a} \: (\beta - x)^b \: \rho(x)^{c} = x^a \: (1-x)^{b} \: (1-\half x)^{c} \\
w^{(a,b)}_P(x) &:= (x - \gamma)^a \: (\delta-x)^b.
\end{cases}
\end{align}
The weight $w^{(b)}_2(x)$ is a still an ultraspherical weight, and the corresponding OPs are the Jacobi polynomials $\{P_n^{(b, b)}\}$. $w^{(a,b,c)}_1(x)$ is the (non-classical) weight for the OPs denoted $\{H_n^{(a, b,c)}\}\). Thus we arrive at the two parameter family of 2D orthogonal polynomials $\{\Pnk\}$ on $\Omega$ given by, for \(0 \le k \le n, \: n = 0,1,2,\dots,\)
\begin{align}
	\Pnk^{(a,b,c)}(x,y) := H_{n-k}^{(c, a, b+k+\half)}(x) \: \rho(x)^k \: P_k^{(b,b)}(\frac{y}{\rho(x)}), \quad (x,y) \in \Omega, 
\end{align}
orthogonal with respect to the weight
\begin{align}
	W^{(a,b,c)}(x,y) &:= w^{(a,b,c)}_H(x) w^{(c,d)}_P(\frac{y}{\rho(x)}) \nonumber \\
	&= x^a \: (1-x)^b \: y^c \: (1-\half x - y)^d, \quad (x,y) \in \Omega.
\end{align}

>>>>

We can further extend this work to trapezium shaped domains. Note that for any trapezium there exists an affine map to the canonical trapezium domain that we consider here, given by
\begin{align}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align}
with 
\begin{align}
\begin{cases}
(\alpha, \beta) &:= (0,1) \\
(\gamma, \delta) &:= (0,1) \\
\rho(x) &:= 1-\half x \\
w^{(a,b,c)}_H(x) &:= (\beta - x)^a \: (x - \alpha)^{b} \: \rho(x)^{c} = (1-x)^{a} \: x^b \: (1-\half x)^{c} \\
w^{(a,b)}_P(x) &:= (\delta-x)^a \: (x - \gamma)^b = (1-x)^a \: x^b.
\end{cases}
\end{align}
The weight $w^{(a,b)}_P(x)$ is the weight for the shifted Jacobi polynomials on the interval $[0,1]$, and hence the corresponding OPs are the shifted Jacobi polynomials $\{\tilde{P}_n^{(a, b)}\}$. We note that the shifted Jacobi polynomials relate the the normal Jacobi polynomials by the relationship $\tilde{P}_n^{(a,b)}(x) = P_n^{(a,b)}(2x-1)$ for any degree $n = 0,1,2,\dots$ and $x \in [0,1]$. $w^{(a,b,c)}_H(x)$ is the (non-classical) weight for the OPs we dentote $\{H_n^{(a,b,c)}\}\). Thus we arrive at the two parameter family of 2D orthogonal polynomials $\{\Pnk\}$ on $\Omega$ given by, for \(0 \le k \le n, \: n = 0,1,2,\dots,\)
\begin{align}
	\Pnk^{(a,b,c,d)}(x,y) := H_{n-k}^{(a, b, c+d+2k+1)}(x) \: \rho(x)^k \: \tilde{P}_k^{(d,c)}(\frac{y}{\rho(x)}), \quad (x,y) \in \Omega, 
\end{align}
orthogonal with respect to the weight
\begin{align}
	W^{(a,b,c,d)}(x,y) &:= w^{(a,b,c+d)}_H(x) \: w^{(d,c)}_P(\frac{y}{\rho(x)}) \nonumber \\
	&= (1-x)^a \: x^b \: y^c \: (1-\half x - y)^d, \quad (x,y) \in \Omega,
\end{align}
i.e. that
\begin{align}
	\int \int_\Omega \Pnk^{(a,b,c,d)} \: P_{m,j}^{(a,b,c,d)} \: W^{(a,b,c,d)} \: \dx \dy &:= C_{n,k}^{(a,b,c,d)} \: \delta_{n,m}
 \: \delta_{j,k},
\end{align}
for some constant $C_{n,k}^{(a,b,c,d)}$.
